---
title: "Well-Mixed Model"
author: "Henry Traynor"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here, we want to determine the behavior of our model in the absence of spatial structure. The only spatially-dependent components of our model is the sorting of immigrants into new roosts and the proportion of fidelitous bats. We augment 'movement2()' to be solely a function of roost occupancy.


no attractiveness from roost size, still cap roost at maximum (try both)
nor spatial structure
set phi max to 100% e.g.

```{r New movement function}
well_mixed_movement <- function(roosts, num_roosts) {
  num_roosts <- length(roosts[,1])
  sample.vec <- function(x, ...) x[sample(length(x), ...)]
  
  #matrix storing num bats in each compartment that leave roost i
  emigrant_bats <- data.frame(
    S = vector("numeric", length=num_roosts),
    I = vector("numeric", length=num_roosts),
    R = vector("numeric", length=num_roosts),
    N = vector("numeric", length=num_roosts)
  )
  #matrix storing num bats that travel to roost i
  immigrant_bats <- data.frame(
    S = vector("numeric", length=num_roosts),
    I = vector("numeric", length=num_roosts),
    R = vector("numeric", length=num_roosts),
    N = vector("numeric", length=num_roosts)
  )
  
  for(i in 1:num_roosts) {
    phi <- 1
    #Number leaving each compartment
    N_e <- rbinom(1, roosts$N[i], phi)
    emigrant_bats$N[i] <- N_e
    if(N_e > 0) {
      x <- c(rep(1, roosts$S[i]),
             rep(2, roosts$I[i]),
             rep(3, roosts$R[i]))
      samp <- sample.vec(x, N_e)
      for(j in 1:N_e) {
        emigrant_bats[i,samp[j]] <- emigrant_bats[i,samp[j]] + 1
        if(emigrant_bats[i,samp[j]] > roosts[i,samp[j]]) {
          browser()
        }
      }
    }
    emigrant_bats$N[i] <- sum(emigrant_bats[i,1:3])
  }
  
  #Subtract these bats from home roost
  roosts[,1:4] <- roosts[,1:4] - emigrant_bats
  
  #Determine which roosts bats are traveling to and store in immigrant_bats
  for(i in 1:num_roosts) {
    pi <- rep(1, num_roosts)
    
    #for loop to set immigration zero for roosts at max occupancy and prevents returning to original roost
    for(k in 1:length(pi)) {
      if(roosts$N[k]>= roosts$N_max[k] || i==k) {
        pi[k] <- 0
      }
    }
    for(k in 1:3) {
      if(emigrant_bats[i,k] != 0) {
        #gives vector of destinations
        destinations <- sample.int(num_roosts,
                                   size=emigrant_bats[i,k],
                                   replace=TRUE,
                                   prob=pi)
        for(j in 1:length(destinations)) {
          immigrant_bats[destinations[j],k] <- immigrant_bats[destinations[j],k] + 1
        }
      }
    }
  }
  
  #Re-tally N for immigrants
  for(i in 1:num_roosts) {
    immigrant_bats$N[i] <- sum(immigrant_bats[i,1:3])
  }
  
  #Add immigrants to new roosts
  roosts[,1:4] <- roosts[,1:4] + immigrant_bats
  
  for(i in 1:num_roosts) {
    for(j in 1:4) {
      if(roosts[i,j] < 0 || is.na(roosts[i,j])) {
        browser()
      }
    }
  }
  return(roosts)
}
```

```{r}
singleDayWellMixed <- function(roosts, roost_parms, SIR_parms) {
  new_roosts <- well_mixed_movement(roosts, num_roosts=roost_parms[1])
  new_roosts <- daytime(new_roosts, roost_parms, SIR_parms)
  return(new_roosts)
}
```

```{r total Vis}
roost_series <- list()
roost_series[[1]] <- roosts
for(i in 2:500) {
  roost_series[[i]] = singleDayWellMixed(roost_series[[i-1]], roost_parms, SIR_parms)
}
roost_vec <- replicate(roost_parms[1], vector("numeric", length=length(roost_series)))

for(i in 1:length(roost_series)) {
  for(j in 1:roost_parms[1]) {
    roost_vec[i,j] = roost_series[[i]]$N[j]
  }
}
colnames(roost_vec) <- paste0("Roost",as.character(seq(1:roost_parms[1])))
roost_vec <- as.data.frame(roost_vec)
roost_vec <- cbind(roost_vec,seq(1:length(roost_vec$Roost1)))
colnames(roost_vec)[length(colnames(roost_vec))] <- "t"

tot <- ggplot(data=roost_vec[1:250,],aes(t)) +
  geom_line(aes(y=Roost1, color="Roost 1")) +
  geom_line(aes(y=Roost2, color="Roost 2")) +
  geom_line(aes(y=Roost3, color="Roost 3")) +
  geom_line(aes(y=Roost4, color="Roost 4")) +
  geom_line(aes(y=Roost5, color="Roost 5")) +
  geom_line(aes(y=Roost6, color="Roost 6")) +
  geom_line(aes(y=Roost7, color="Roost 7")) +
  geom_line(aes(y=Roost8, color="Roost 8")) +
  geom_line(aes(y=Roost9, color="Roost 9")) +
  geom_line(aes(y=Roost10, color="Roost 10")) +
  ylab("Roost Occupancy") + xlab("Time (Days)") +
  labs(colour="Roost #") +
  ggtitle("Total Roost Occupancy")+ theme(legend.position="none")
```

```{r % occupancy}
roost_vecP <- replicate(roost_parms[1], vector("numeric", length=length(roost_series)))

for(i in 1:length(roost_series)) {
  for(j in 1:roost_parms[1]) {
    roost_vecP[i,j] = roost_series[[i]]$N[j]/roost_series[[i]]$N_max[j]
  }
}
colnames(roost_vecP) <- paste0("Roost",as.character(seq(1:roost_parms[1])))
roost_vecP <- as.data.frame(roost_vecP)
roost_vecP <- cbind(roost_vecP,seq(1:length(roost_vecP$Roost1)))
colnames(roost_vecP)[length(colnames(roost_vecP))] <- "t"

prop <- ggplot(data=roost_vecP[1:250,],aes(t)) +
  geom_line(aes(y=Roost1, color="Roost 1")) +
  geom_line(aes(y=Roost2, color="Roost 2")) +
  geom_line(aes(y=Roost3, color="Roost 3")) +
  geom_line(aes(y=Roost4, color="Roost 4")) +
  geom_line(aes(y=Roost5, color="Roost 5")) +
  geom_line(aes(y=Roost6, color="Roost 6")) +
  geom_line(aes(y=Roost7, color="Roost 7")) +
  geom_line(aes(y=Roost8, color="Roost 8")) +
  geom_line(aes(y=Roost9, color="Roost 9")) +
  geom_line(aes(y=Roost10, color="Roost 10")) +
  ylab("Roost Occupancy") + xlab("Time (Days)") +
  labs(colour="Roost #") +
  ggtitle("% Roost Occupancy")+ theme(legend.position="none")
```

```{r Susc. Vis}
roost_vecS <- replicate(roost_parms[1], vector("numeric", length=length(roost_series)))

for(i in 1:length(roost_series)) {
  for(j in 1:roost_parms[1]) {
    roost_vecS[i,j] = roost_series[[i]]$S[j]
  }
}
colnames(roost_vecS) <- paste0("Roost",as.character(seq(1:roost_parms[1])))
roost_vecS <- as.data.frame(roost_vecS)
roost_vecS <- cbind(roost_vecS,seq(1:length(roost_vecS$Roost1)))
colnames(roost_vecS)[length(colnames(roost_vecS))] <- "t"

susc <- ggplot(data=roost_vecS[1:250,],aes(t)) +
  geom_line(aes(y=Roost1, color="Roost 1")) +
  geom_line(aes(y=Roost2, color="Roost 2")) +
  geom_line(aes(y=Roost3, color="Roost 3")) +
  geom_line(aes(y=Roost4, color="Roost 4")) +
  geom_line(aes(y=Roost5, color="Roost 5")) +
  geom_line(aes(y=Roost6, color="Roost 6")) +
  geom_line(aes(y=Roost7, color="Roost 7")) +
  geom_line(aes(y=Roost8, color="Roost 8")) +
  geom_line(aes(y=Roost9, color="Roost 9")) +
  geom_line(aes(y=Roost10, color="Roost 10")) +
  ylab("Roost Susc. Population") + xlab("Time (Days)") +
  labs(colour="Roost #") +
  ggtitle("Susceptible Population")+ theme(legend.position="none")
```

```{r Inf. Vis}
roost_vecI <- replicate(roost_parms[1], vector("numeric", length=length(roost_series)))

for(i in 1:length(roost_series)) {
  for(j in 1:roost_parms[1]) {
    roost_vecI[i,j] = roost_series[[i]]$I[j]
  }
}
colnames(roost_vecI) <- paste0("Roost",as.character(seq(1:roost_parms[1])))
roost_vecI <- as.data.frame(roost_vecI)
roost_vecI <- cbind(roost_vecI,seq(1:length(roost_vecI$Roost1)))
colnames(roost_vecI)[length(colnames(roost_vecI))] <- "t"

inft <- ggplot(data=roost_vecI[1:250,],aes(t)) +
  geom_line(aes(y=Roost1, color="Roost 1")) +
  geom_line(aes(y=Roost2, color="Roost 2")) +
  geom_line(aes(y=Roost3, color="Roost 3")) +
  geom_line(aes(y=Roost4, color="Roost 4")) +
  geom_line(aes(y=Roost5, color="Roost 5")) +
  geom_line(aes(y=Roost6, color="Roost 6")) +
  geom_line(aes(y=Roost7, color="Roost 7")) +
  geom_line(aes(y=Roost8, color="Roost 8")) +
  geom_line(aes(y=Roost9, color="Roost 9")) +
  geom_line(aes(y=Roost10, color="Roost 10")) +
  ylab("Roost Inf. Population") + xlab("Time (Days)") +
  labs(colour="Roost #") +
  ggtitle("Infected Population")+ theme(legend.position="none")
```

```{r Rec. Vis}
roost_vecR <- replicate(roost_parms[1], vector("numeric", length=length(roost_series)))

for(i in 1:length(roost_series)) {
  for(j in 1:roost_parms[1]) {
    roost_vecR[i,j] = roost_series[[i]]$R[j]
  }
}
colnames(roost_vecR) <- paste0("Roost",as.character(seq(1:roost_parms[1])))
roost_vecR <- as.data.frame(roost_vecR)
roost_vecR <- cbind(roost_vecR,seq(1:length(roost_vecR$Roost1)))
colnames(roost_vecR)[length(colnames(roost_vecR))] <- "t"

recv <- ggplot(data=roost_vecR[1:250,],aes(t)) +
  geom_line(aes(y=Roost1, color="Roost 1")) +
  geom_line(aes(y=Roost2, color="Roost 2")) +
  geom_line(aes(y=Roost3, color="Roost 3")) +
  geom_line(aes(y=Roost4, color="Roost 4")) +
  geom_line(aes(y=Roost5, color="Roost 5")) +
  geom_line(aes(y=Roost6, color="Roost 6")) +
  geom_line(aes(y=Roost7, color="Roost 7")) +
  geom_line(aes(y=Roost8, color="Roost 8")) +
  geom_line(aes(y=Roost9, color="Roost 9")) +
  geom_line(aes(y=Roost10, color="Roost 10")) +
  ylab("Roost Inf. Population") + xlab("Time (Days)") +
  labs(colour="Roost #") +
  ggtitle("Recovered Population")+ theme(legend.position="none")
```

```{r Visualization}
library(gridExtra)
grid.arrange(tot, prop,susc, inft, recv)

```

