---
title: "Untitled"
author: "Henry Traynor"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

We want to compare SIR vs SIRS dynamics across gradients of urbanization and correlated spatial statistics. We will generate a gradient of modern structures in a landscape crossed with a gradient of a given spatial statistic. Running simulated epidemics on this landscape with SIR and SIRS dynamics reveals the significance of metapopulation dynamics in viral transmission.


```{r Sourcing}
files_functions <- list.files(path = "C:/Users/henry/Molossid_Transmission/Functions", pattern = "\\.R$", full.names = TRUE)
for(file in files_functions) {
  source(file)
}
```

```{r Landscapes}
num_roosts <- 100

#sequence giving proportion of modern buildings gradient
modern_range <- c(0,1)
modern_resolution <- .075
prop_modern_seq <- seq(modern_range[1], modern_range[2], by=modern_resolution)

#seq for number of clusters
cluster_range <- c(1,round(num_roosts/4)) # more clusters means lower Moran's I
cluster_resolution <- 2
cluster_seq <- seq(cluster_range[1], cluster_range[2], by=cluster_resolution)

#seq for x,y sd of clusters
sd_range <- c(0.03, 0.2) #higher sd correlates to lower Moran's I
sd_seq <- seq(sd_range[1], sd_range[2], length=length(cluster_seq))

spatial_var <- data.frame(num_clusters = cluster_seq,
                          sd = sd_seq)

num_maps <- length(prop_modern_seq)*length(cluster_seq)
total_num_roosts <- num_maps*num_roosts

roost_crossed_gradient <- data.frame(map_ID = rep(1:num_maps, each=num_roosts),
                                     x = vector("numeric", length=total_num_roosts),
                                     y = vector("numeric", length=total_num_roosts),
                                     isModern = vector("numeric", length=total_num_roosts),
                                     N_max = vector("numeric", length=total_num_roosts))

spatial_var_combos <- data.frame(prop_modern = rep(prop_modern_seq, length(cluster_seq)))
spatial_var_combos$num_clusters <- rep(cluster_seq, each=length(prop_modern_seq))
spatial_var_combos$sd <- rep(sd_seq, each=length(prop_modern_seq))
spatial_var_combos$Clark_Evans_R <- vector("numeric", length(spatial_var_combos$prop_modern))

for(i in 1:length(spatial_var_combos$prop_modern)) {
  roost_parms <- c(num_roosts = num_roosts,  # number of roosts
                   num_clusters = spatial_var_combos$num_clusters[i], # number of clusters
                   sd = spatial_var_combos$sd[i],
                   prop_modern = spatial_var_combos$prop_modern[i])     # standard distance from cluster center
  map <- roostMapProp(roost_parms)
  map <- map[, !names(map) %in% c("bin")]
  firstIndex <- which(roost_crossed_gradient$map_ID == i)[1]
  roost_crossed_gradient[firstIndex:(firstIndex +nrow(map)-1), -1] <- map
}

library(spatstat.geom)
library(spatstat.explore)
for(i in 1:length(spatial_var_combos$prop_modern)) {
  map <- roost_crossed_gradient[roost_crossed_gradient$map_ID==i,]
  pp <- ppp(map$x, map$y)
  spatial_var_combos$Clark_Evans_R[i] <- clarkevans(pp)["cdf"]
}
```

```{r Infection Parameters}
SIR_parms  <- c(beta = 0.1,   # transmission rate
                gamma = 0.03) # recovery rate

SIRS_parms <- c(beta = 0.1,   # transmission rate
                gamma = 0.03, # recovery rate
                omega = 0.01) # loss of immunity
```

```{r SIRS sim}
sim_list_SIR <- list()
map_intensity_SIR <- c()

sim_list_SIRS <- list()
map_intensity_SIRS <- c()

start_time <- Sys.time()

sim_list_list_SIR <- list()

for(map_num in unique(roost_crossed_gradient$map_ID)) {
  roost_parms[1] <- num_roosts
  num_days <- 500
  
  roost_map <- roost_crossed_gradient[roost_crossed_gradient$map_ID == map_num,]
  roost_dist <- distMatrix(num_roosts, roost_map)
  
  roosts <- data.frame(
    S = vector("numeric", length=roost_parms[1]),
    I = vector("numeric", length=roost_parms[1]),
    R = vector("numeric", length=roost_parms[1]),
    N = vector("numeric", length=roost_parms[1]),
    N_max = roost_map$N_max
  )

  #Populate Roosts
  roosts$N <- round(roosts$N_max/1.5)
  roosts$S <- roosts$N
  roosts$S[1] <- roosts$S[1]-1
  roosts$I <- roosts$N-roosts$S

  #Total distances between any 2 roosts
  total_dist <- 0
  for(i in 1:roost_parms[1]) {
    for(j in 1:i) {
      total_dist <- total_dist + as.numeric(roost_dist[i,j])
    }
  }

  #Score, a measure of isolation. greater score ==> greater isolation
  scores <- vector("numeric", length=roost_parms[1])
  for(i in 1:roost_parms[1]) {
    tot <- sum(roost_dist[i,])
    scores[i] <- tot/total_dist
  }
  
  sim_list_SIR[[1]] <- roosts
  sim_list_SIRS[[1]] <- roosts
  for(i in 2:num_days) {
    sim_list_SIR[[i]] <- singleDay(sim_list_SIR[[i-1]], 
                               roost_dist, 
                               roost_parms, 
                               SIRS_parms, 
                               model="SIR", 
                               scores, 
                               phi_max=0.25)
    sim_list_SIRS[[i]] <- singleDay(sim_list_SIRS[[i-1]], 
                               roost_dist, 
                               roost_parms, 
                               SIRS_parms, 
                               model="SIRS", 
                               scores, 
                               phi_max=0.25)
  }
  
  inf_sums_SIR <- c()
  inf_sums_SIRS <- c()
  for(i in 1:length(sim_list_SIR)) {
    inf_sums_SIR[i] <- sum(sim_list_SIR[[i]]$I)
    inf_sums_SIRS[i] <- sum(sim_list_SIRS[[i]]$I)
  }
  map_intensity_SIR[map_num] <- max(inf_sums_SIR)
  map_intensity_SIRS[map_num] <- max(inf_sums_SIRS)
  
  # compute elapsed time
  elapsed <- Sys.time() - start_time
  
  # print progress
  cat("Iteration:", map_num, " of  ", length(unique(roost_crossed_gradient$map_ID)),
      "| Elapsed time:", round(elapsed, 2), "\n")
}

map_pop_size <- c()

for(i in 1:length(map_intensity_SIR)) {
  roost_map <- roost_crossed_gradient[roost_crossed_gradient$map_ID == i,]
  map_pop_size[i] <- round(sum(roost_map$N_max)/1.5)
}

spatial_var_combos$SIRS_intensity <- map_intensity_SIRS
spatial_var_combos$SIR_intensity <- map_intensity_SIR

spatial_var_combos$SIR_prevalence <- spatial_var_combos$SIR_intensity / map_pop_size
spatial_var_combos$SIRS_prevalence <- spatial_var_combos$SIRS_intensity / map_pop_size
```

```{r heatmaps short}
library(ggplot2)
library(akima)
library(gridExtra)

#remove outliers (no significant epidemic takes hold)
spatial_var_combos_clean <- subset(spatial_var_combos, SIRS_prevalence >= 0.05)

interp_res_SIR <- with(spatial_var_combos_clean, interp(x = prop_modern, y = Clark_Evans_R, z = SIR_prevalence))

interp_df_SIR <- with(interp_res_SIR, expand.grid(x = x, y = y))
interp_df_SIR$z <- as.vector(interp_res_SIR$z)

SIR_interp_plot <- ggplot(interp_df_SIR, aes(x, y, fill = z)) +
  geom_raster() +
  scale_fill_viridis_c() +
  theme_minimal() +
  xlab("Proportion modern buildings") +
  ylab("Clark Evan's R") +
  labs(fill = "Peak prevalance") + 
  ggtitle("SIR Dynamics")

interp_res_SIRS <- with(spatial_var_combos_clean, interp(x = prop_modern, y = Clark_Evans_R, z = SIRS_prevalence))

interp_df_SIRS <- with(interp_res_SIRS, expand.grid(x = x, y = y))
interp_df_SIRS$z <- as.vector(interp_res_SIRS$z)

SIRS_interp_plot <- ggplot(interp_df_SIRS, aes(x, y, fill = z)) +
  geom_raster() +
  scale_fill_viridis_c() +
  theme_minimal() +
  xlab("Proportion modern buildings") +
  ylab("Clark Evan's R") +
  labs(fill = "Peak prevalance") +
  ggtitle("SIRS Dynamics")

SIR_vs_SIRS_heatmap <- grid.arrange(SIR_interp_plot, SIRS_interp_plot)
#saves into "FigureSaves" folder in "Markdowns" folder
ggsave("FigureSaves/SIR_vs_SIRS_heatmap.png", plot = SIR_vs_SIRS_heatmap,
       width = 6,
       height = 4,
       dpi = 300)
```

```{r Spatial Structure Effect}
model_SIR <- lm(SIR_prevalence ~ prop_modern + Clark_Evans_R, data = spatial_var_combos_clean)
summary(model_SIR)

model_SIRS <- lm(SIRS_prevalence ~ prop_modern + Clark_Evans_R, data = spatial_var_combos_clean)
summary(model_SIR)
```
