---
title: "Untitled"
author: "Henry Traynor"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

We want to compare SIR vs SIRS dynamics across gradients of urbanization and correlated spatial statistics. We will generate a gradient of modern structures in a landscape crossed with a gradient of a given spatial statistic. Running simulated epidemics on this landscape with SIR and SIRS dynamics reveals the significance of metapopulation dynamics in viral transmission.


```{r Sourcing}
files_functions <- list.files(path = "C:/Users/henry/Molossid_Transmission/Functions", pattern = "\\.R$", full.names = TRUE)
for(file in files_functions) {
  source(file)
}
```

```{r Landscapes}
num_roosts <- 100

#sequence giving proportion of modern buildings gradient
modern_range <- c(0,1)
modern_resolution <- .1
prop_modern_seq <- seq(modern_range[1], modern_range[2], by=modern_resolution)

#seq for number of clusters
cluster_range <- c(1,round(num_roosts/4)) # more clusters means lower Moran's I
cluster_resolution <- 2
cluster_seq <- seq(cluster_range[1], cluster_range[2], by=cluster_resolution)

#seq for x,y sd of clusters
sd_range <- c(0.03, 0.2) #higher sd correlates to lower Moran's I
sd_seq <- seq(sd_range[1], sd_range[2], length=length(cluster_seq))

spatial_var <- data.frame(num_clusters = cluster_seq,
                          sd = sd_seq)

num_maps <- length(prop_modern_seq)*length(cluster_seq)
total_num_roosts <- num_maps*num_roosts

roost_crossed_gradient <- data.frame(map_ID = rep(1:num_maps, each=num_roosts),
                                     x = vector("numeric", length=total_num_roosts),
                                     y = vector("numeric", length=total_num_roosts),
                                     isModern = vector("numeric", length=total_num_roosts),
                                     N_max = vector("numeric", length=total_num_roosts))

spatial_var_combos <- data.frame(prop_modern = rep(prop_modern_seq, length(cluster_seq)))
spatial_var_combos$num_clusters <- rep(cluster_seq, each=length(prop_modern_seq))
spatial_var_combos$sd <- rep(sd_seq, each=length(prop_modern_seq))
spatial_var_combos$Clark_Evans_R <- vector("numeric", length(spatial_var_combos$prop_modern))

for(i in 1:length(spatial_var_combos$prop_modern)) {
  roost_parms <- c(num_roosts = num_roosts,  # number of roosts
                   num_clusters = spatial_var_combos$num_clusters[i], # number of clusters
                   sd = spatial_var_combos$sd[i],
                   prop_modern = spatial_var_combos$prop_modern[i])     # standard distance from cluster center
  map <- roostMapProp(roost_parms)
  map <- map[, !names(map) %in% c("bin")]
  firstIndex <- which(roost_crossed_gradient$map_ID == i)[1]
  roost_crossed_gradient[firstIndex:(firstIndex +nrow(map)-1), -1] <- map
}

library(spatstat.geom)
library(spatstat.explore)
for(i in 1:length(spatial_var_combos$prop_modern)) {
  map <- roost_crossed_gradient[roost_crossed_gradient$map_ID==i,]
  pp <- ppp(map$x, map$y)
  spatial_var_combos$Clark_Evans_R[i] <- clarkevans(pp)["cdf"]
}
```

```{r Infection Parameters}
SIR_parms  <- c(beta = 0.1,   # transmission rate
                gamma = 0.03) # recovery rate

SIRS_parms <- c(beta = 0.1,   # transmission rate
                gamma = 0.03, # recovery rate
                omega = 0.01) # loss of immunity
```

```{r SIR sim}
sim_list <- list()
map_intensity <- c()

for(map_num in unique(roost_crossed_gradient$map_ID)) {
  roost_parms[1] <- num_roosts
  num_days <- 100
  
  roost_map <- roost_crossed_gradient[roost_crossed_gradient$map_ID == roost_num,]
  roost_dist <- distMatrix(num_roosts, roost_map)
  
  roosts <- data.frame(
    S = vector("numeric", length=roost_parms[1]),
    I = vector("numeric", length=roost_parms[1]),
    R = vector("numeric", length=roost_parms[1]),
    N = vector("numeric", length=roost_parms[1]),
    N_max = roost_map$N_max
  )

  #Populate Roosts
  roosts$N <- round(roosts$N_max/1.5)
  roosts$S <- roosts$N
  roosts$S[1] <- roosts$S[1]-1
  roosts$I <- roosts$N-roosts$S

  #Total distances between any 2 roosts
  total_dist <- 0
  for(i in 1:roost_parms[1]) {
    for(j in 1:i) {
      total_dist <- total_dist + as.numeric(roost_dist[i,j])
    }
  }

  #Score, a measure of isolation. greater score ==> greater isolation
  scores <- vector("numeric", length=roost_parms[1])
  for(i in 1:roost_parms[1]) {
    tot <- sum(roost_dist[i,])
    scores[i] <- tot/total_dist
  }
  
  sim_list[[1]] <- roosts
  for(i in 2:num_days) {
    sim_list[[i]] <- singleDay(roosts, 
                               roost_dist, 
                               roost_parms, 
                               SIR_parms, 
                               model="SIR", 
                               scores, 
                               phi_max=0.25)
  }
  
  inf_sums <- c()
  for(i in 1:length(sim_list)) {
    inf_sums[i] <- sum(sim_list[[i]]$I)
  }
  map_intensity[map_num] <- max(inf_sums)
}
```

```{r SIRS sim}
sim_list <- list()
map_intensity_SIRS <- c()

for(map_num in unique(roost_crossed_gradient$map_ID)) {
  roost_parms[1] <- num_roosts
  num_days <- 100
  
  roost_map <- roost_crossed_gradient[roost_crossed_gradient$map_ID == roost_num,]
  roost_dist <- distMatrix(num_roosts, roost_map)
  
  roosts <- data.frame(
    S = vector("numeric", length=roost_parms[1]),
    I = vector("numeric", length=roost_parms[1]),
    R = vector("numeric", length=roost_parms[1]),
    N = vector("numeric", length=roost_parms[1]),
    N_max = roost_map$N_max
  )

  #Populate Roosts
  roosts$N <- round(roosts$N_max/1.5)
  roosts$S <- roosts$N
  roosts$S[1] <- roosts$S[1]-1
  roosts$I <- roosts$N-roosts$S

  #Total distances between any 2 roosts
  total_dist <- 0
  for(i in 1:roost_parms[1]) {
    for(j in 1:i) {
      total_dist <- total_dist + as.numeric(roost_dist[i,j])
    }
  }

  #Score, a measure of isolation. greater score ==> greater isolation
  scores <- vector("numeric", length=roost_parms[1])
  for(i in 1:roost_parms[1]) {
    tot <- sum(roost_dist[i,])
    scores[i] <- tot/total_dist
  }
  
  sim_list[[1]] <- roosts
  for(i in 2:num_days) {
    sim_list[[i]] <- singleDay(roosts, 
                               roost_dist, 
                               roost_parms, 
                               SIRS_parms, 
                               model="SIRS", 
                               scores, 
                               phi_max=0.25)
  }
  
  inf_sums <- c()
  for(i in 1:length(sim_list)) {
    inf_sums[i] <- sum(sim_list[[i]]$I)
  }
  map_intensity[map_num] <- max(inf_sums)
  if(map_num == 35) { break }
}
```

```{r heatmaps short}
map_intensity_SIRS <- vector("numeric", length=length(spatial_var_combos$prop_modern))
for(i in 1:length(map_intensity)) {
  map_intensity_SIRS[i] <- map_intensity[i]
}
spatial_var_combos$SIRS_intensity <- map_intensity_SIRS

library(ggplot2)
ggplot(spatial_var_combos, aes(prop_modern, Clark_Evans_R, color=SIRS_intensity)) + geom_point()
```
